Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-16 latex/tex/experiments.tex
performance preamble updates

\subsection{Performance}
\label{sec:perf}
For all hierarchical clustering experiments in this section, the number of tree leaf nodes $k$ was set at $100$, the tolerance
for the power iteration was set at $0$, and only complete levels were considered for analysis purposes for both level and strong scaling plots.

>>>>

\subsection{Performance}
\label{sec:perf}
For all hierarchical clustering experiments in this section, the number of tree leaf nodes $k$ was set at $100$, 
the number of NMF iterations was set to $100$,
the power iteration was allowed to stop iterating after convergence,
and only complete levels were considered for analysis purposes for both level and strong scaling plots.
